\section*{Problem 2: Soft Margin Hyperplanes [9 points]}
The soft-margin primal SVM problem is:

\begin{align}\label{eqn:soft-svm}\text{min} \frac{1}{2} ||\textbf{w}||_2^2 + C \sum_{i=1}^N \xi^{(i)} \end{align}

subject to feasibility constraints that for all $i=1,...,N$:

$$y^{(i)}(\textbf{w}^T \xv^{(i)} + b) \geq 1 - \xi^{(i)}$$
$$\xi^{(i)} \geq 0$$

Suppose instead the optimization objective was  changed to $\frac{1}{2}||\textbf{w}||_2^2 + C \sum_{i=1}^N \xi^{(i)}^2$ while the feasibility constraints are kept the same. 

\textbf{Hint}: Before attempting this problem, we highly recommend first trying to derive the dual formulations for the hard-margin and soft-margin SVMs presented in class by working through the steps detailed below.

\begin{enumerate}
\item \textbf{[2pts]} \textbf{Short Answer: }
         How is the penalty changed (relative to the original formulation \ref{eqn:soft-svm}) for points within the margin? How about misclassified points?
        
 
    \begin{tcolorbox}[fit,height=4cm, width=15cm, blank, borderline={1pt}{-2pt},nobeforeafter]
        %solution
    \end{tcolorbox}
    
    
\item \textbf{[1 pt]} Incorporate the feasibility constraints into the objective function using the method of Lagrange multipliers by writing out the Lagrangian and the associated constraints. 

\begin{tcolorbox}[fit,height=5.0cm, width=0.95\textwidth, blank, borderline={1pt}{-2pt}]
%solution 
\end{tcolorbox}

% \newpage 

\item \textbf{[3 pts]} Next, take the partial derivative of the Lagrangian with respect to all of the optimization variables. Be sure to show all of you work.

\begin{tcolorbox}[fit,height=21.0cm, width=0.95\textwidth, blank, borderline={1pt}{-2pt}]
%solution 
\end{tcolorbox}

\newpage
\item \textbf{[3 pts]} Finally, by setting the partial derivatives from the previous part equal to 0, derive the dual formulation of SVMs in this general case. Again, be sure to show all of you work.


\begin{tcolorbox}[fit,height=18.0cm, width=0.95\textwidth, blank, borderline={1pt}{-2pt}]
%solution 
\end{tcolorbox}

\end{enumerate}





